---
title: "Ground breaking research!"
author: |
  | Kirien Whan$^1$ and Famous Collaborators$^2$
  | 1. KNMI
  | 2. University
date: "January 25, 2018"
output:
  pdf_document:
    includes:
      in_header: extra_texinfo.tex
    keep_tex: yes
    number_sections: no
  html_document: default
bibliography: Your.bib
abstract: |
  The abstract text goes here....
---

<!-- 
You can include comments.

I downloaded data from: www.data.com

I preprocessed it with the script: ./dddd/

To render this document: 
R --no-save --no-restore -e "require(rmarkdown); render('example.Rmd')"

-->


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval=TRUE,include=TRUE, fig.width = 6, fig.height = 4, 
                      cache=TRUE, warnings=FALSE)

options(figcap.prefix = "Figure", figcap.sep = ":", figcap.prefix.highlight="**")
options(tabcap.prefix = "Table", tabcap.sep = ":", tabcap.prefix.highlight="**")

```


```{r global_options, include=FALSE}
library(ggplot2)
library(xtable)

source("functions_markdownCrossRef.R")

source("./example_script.r")

```

```{r importData, include=FALSE}

ENSO <- rnorm(50, 0, 3)

temp <- rnorm(50, 25, 10)


```

```{r calcCorrel, include=FALSE}

ensoCor <- cor(ENSO, temp, use="complete.obs")
  
  
```


```{r calcLEN, include=FALSE}
# Do some other calculations:
len <- length(ENSO)

```


# Introduction

Citing my own work [@whan2015impact]. Can also use latex citations, but then you need to run bibtex etc \citep{whan2015impact}.

# Data and Methods

You can call R directly in-line like this, e.g. We use `r length(ENSO)` years of data. Or you can call objects that have been defined in previous chunks like this, e.g. We use `r len` years of data. 

Including latex code directly is easy using dollar signs, e.g. The Ni&#241;o 3.4 index is the area averaged standardized SST anomalies from the tropical Pacific (5$^{\circ}$N-5$^{\circ}$S, 170$^{\circ}$W-120$^{\circ}$W)

Referencing equations is easy as well since we can include latex code directly. See equation @eq1:

(@eq1) $$  ONETHING  = \max\limits_{j=1,..k}[OF.SOME.OTHER.THINGS] $$

# Results

There are built in ways to do figure cross-referencing, but I found this method best (using functions imported from the script "functions_markdownCrossRef.R") (`r figRef("CorPlot")`). Referencing tables is done like this (`r tabRef("xtable_table1")`).

We find a relationship between ENSO and temperature (r = `r round(ensoCor, 2)`).

# Conclusions

# References


```{r table1, results="asis", include=FALSE}

# I use xtable for including tables:
  Tabdf <- data.frame(Name=c("cor1", "cor2"),
		     Resolution = c(round(ensoCor, 2), 0.8))
  colnames(Tabdf) <- c("Name", "Correlation") 
  tabcap <- "A table caption"
  Tabout <- xtable(Tabdf, caption=tabcap, digits=2)
  align(Tabout) <- "lcc"
  print(Tabout, comment=F, caption.placement = 'top', include.rownames=FALSE)
  
```



```{r makeplot, echo=FALSE, fig.cap=figRef("CorPlot", "The Correlation between ENSO and Temp")}

aplot <- ggplot(data=data.frame(temp, ENSO)) +
geom_line(aes(x=ENSO, y=temp))  

aplot

```

